\NOTOPPER{Acknowledgements}
\chapter*{Acknowledgements}

It has been a privilege to be a part of the nascent field of
gravitational wave astronomy at this exciting time, perhaps at the
cusp before an era of discovery.  It would be impossible to properly
acknowledge all of the great people I have encountered and who have
influenced me during my time in graduate school, but I will nonetheless
try to name the main characters.

Thank you to Adrian Melissinos, my advisor at the University of
Rochester, for your energy and creativity, and for getting me involved
with gravitational waves in the first place.  

To Rana Adhikari, my mentor at Caltech and a driving force behind
Enhanced LIGO, for showing me how to align the mode cleaner and cut
the can off of photodiodes.
%, solder
%tiny parts, and brew acceptable coffee.

To Valery Frolov at LIGO Livingston, a tireless commissioner and
uncompromising scientist, for mentoring me and for countless late
night hours in the control room.

To Gabriela Gonz\'alez, my advisor at Louisiana State University, for
adopting me as a student and guiding me through the graduate school
process with the utmost patience, and for letting us drink Jorge's
whiskey.

And to Rai Weiss, a role model for us all.

Thank you also to my fellow graduate students and friends, among them
Kate Dooley, Stefanos Giampanis, Ryan Dahl, Lisa Togler, Kris Yirak,
Aimee Slaughter, Bree Lupia, Matthew Bryant, and Sara DeRosier.  To
my cohort at LSU: Anamaria Effler, Ryan DeRosa, Chad Hanna, Jeff
Kissel, Jake Slutsky, Rupal Amin, and Sarah Caudhill.  To Rob Ward,
Marie-H\'el\`ene, Jeff Smith, Dan Busby, Phil Willems, Steve Vass, and
John Miller for making my stay at Caltech an enjoyable one.  And to
everyone else who worked on the Enhanced LIGO project or continues to
work towards the detection of graviational waves.

%\NOTOPPER{Preface}
%\chapter*{Preface}

Finally, the boilerplate: this work was supported by the National
Science Foundation under grant
\href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0905184}{PHY-0905184}.
LIGO was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National
Science Foundation and operates under cooperative agreement
\href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0757058}{PHY-0757058}.
This dissertation has LIGO Document number LIGO-P1000010.

